\documentclass[10pt,letterpaper,sans]{moderncv}

\moderncvtheme[blue]{casual}
\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\recomputelengths{}

\firstname{Wolf}
\familyname{Honor\'{e}}
\mobile{(210)~979~1509}
\email{wolfhonore@gmail.com}
\social[github]{whonore}
\social[googlescholar]{wolf.honore}
\social[linkedin]{whonore}
\homepage{whonore.github.io}

\begin{document}

\newcommand{\about}{\raisebox{0.25ex}{\scalebox{0.7}{$\sim$}}}
\newcommand{\ormore}{\raisebox{0.25ex}{+}}

\renewcommand*{\namefont}{\fontsize{20}{24}\mdseries\upshape}
\makecvtitle{}
\vspace{-1cm}

\section{Education}

\cventry{2016--2022}
        {PhD Computer Science}
        {Yale University}
        {}
        {}
        {Advised by: Zhong Shao}
\cventry{2012--2016}
        {BA Computer Science/BS Applied Math}
        {University of Rochester}
        {}
        {GPA:\@ \textit{3.98/4.00}}
        {Graduated \textit{Summa Cum Laude}}

\section{Industry Experience}

\cventry{September 2024--Present}
        {Applied Scientist}
        {Amazon --- Automated Reasoning in Identity}
        {Santa Clara, CA}
        {}
        {%
        }
\cventry{July 2022 -- September 2024}
        {Staff Research Engineer}
        {CertiK}
        {Remote}
        {}
        {%
          \begin{itemize}
            \item
              Developed a suite of tools to automatically translate Solidity
              code annotated with a custom formal specification language into an
              equivalent Dafny model.
            \item
              Contributed to a VSCode extension and language server that
              integrates with the verification tools to provide a better user
              experience.
            \item
              Worked with a remote team of auditors to train them in writing
              specifications for client projects.
            \item
              Helped to scale formal verification capabilities by developing a
              procedure and training resources for using the verification tools
              and integrating the results into audit reports.
            \item
              Verified client blockchain and smart contract projects in a
              variety of languages, including Solidity, Move, Rust, and Haskell.
          \end{itemize}
        }
\cventry{Summer 2019 (Internship)}
        {Formal Verification Engineer}
        {SiFive}
        {San Mateo, CA}
        {}
        {%
          \begin{itemize}
            \item
              Formalized and partially verified a cache coherence algorithm
              using the Kami Coq framework.
          \end{itemize}
        }
\cventry{Summer 2014, 2015, 2016 (Internship)}
        {Student Analyst}
        {Southwest Research Institute}
        {San Antonio, TX}
        {}
        {%
          \begin{itemize}
            \item
              Created a program to generate complex data for training and
              testing machine learning particle swarm optimization.
            \item
              Created a program to consolidate documentation from heterogeneous
              sources (DOCX, PDF, code comments, etc.) into HTML\@.
            \item
              Developed a tool-chain to convert raw GIS data into customizable
              MapServer maps.
        \end{itemize}
        }

\section{Open Source Projects}

\cventry{2017--Present}
        {Coqtail}
        {Creator/Maintainer}
        {\httpslink{github.com/whonore/Coqtail}}
        {}
        {%
          \begin{itemize}
            \item
              A popular Vim plugin that interfaces with the Coq proof assistant
              to provide an IDE experience similar to CoqIDE, ProofGeneral, or VSCoq.
            \item
              Over 7 years old, 250\ormore{} stars, \about{}70 PRs from contributors.
          \end{itemize}
        }
\cventry{2020}
        {New Haven Help With COVID}
        {Contributor/Lead Web Developer}
        {\httpslink{github.com/newhaven-helpwithcovid/covid-volunteers}}
        {}
        {%
          \begin{itemize}
            \item
              A Ruby on Rails website to help match volunteers with
              opportunities in New Haven during the peak of the COVID-19 pandemic.
            \item
              Managed a small team of remote student developers.
            \item
              Handled website and database deployment (Postgres) and maintenance.
          \end{itemize}
        }

\section{Research Projects}

\cventry{2022}
        {Byzantine Atomic Distributed Objects}
        {Yale University}
        {Advised by: Zhong Shao}
        {}
        {%
          Generalized the Atomic Distributed Object model to support liveness
          reasoning as well as both benign and byzantine fault tolerant
          protocols through configurable quorum definitions.
          Completed the first mechanized safety and liveness proofs for this
          generalized fault model and proved that a Coq specification of a
          variant of Jolteon refines the model.
        }
\cventry{2021--2022}
        {Reconfigurable Atomic Distributed Objects}
        {Yale University}
        {Advised by: Zhong Shao}
        {}
        {%
          Extended the Atomic Distributed Object model with additional metadata
          to enable simple verification of protocol-level safety properties.
          Completed the first mechanized safety proof for a reconfigurable
          consensus protocol by showing that a Coq specification of a Raft-like
          protocol refines the model.
        }
\cventry{2018--2021}
        {Atomic Distributed Objects}
        {Yale University}
        {Advised by: Zhong Shao}
        {}
        {%
          Developed a general framework for distributed application verification
          in Coq based on a novel abstraction that models systems as a tree of
          committed and uncommitted commands that can be atomically manipulated.
          Proved the correctness of several non-trivial distributed
          applications, and showed that many common protocols (e.g., Paxos
          variants, Chain Replication) refine this model.
        }
\cventry{2018--2021}
        {Deep Spec Web Server}
        {Yale University}
        {In collaboration with: University of Pennsylvania, Princeton University}
        {}
        {%
          Extended CertiKOS with an unverified socket layer to run a verified
          web server written in C.
          Proved the soundness of the web server's user-level axiomatized system
          call specifications with respect to CertiKOS' kernel-level specifications.
        }
\cventry{2017--2018}
        {690 Project (Qualifying Exam Project)}
        {Yale University}
        {Advised by: Zhong Shao}
        {}
        {%
          Verified a C implementation of the WormSpace distributed system in Coq
          using Certified Concurrent Abstraction Layers.
          Extended CertiKOS with unverified networking support using the lwIP
          library in order to run WormSpace.
        }
\cventry{Spring 2016}
        {Statically Detecting Rootkits (Independent Study)}
        {University of Rochester}
        {Advised by: John Criswell}
        {}
        {%
          Created an LLVM compiler pass to statically detect potentially
          malicious kernel modules by searching for comparisons between pointers
          and system call addresses.
        }

\section{Teaching Experience}

\cventry{Fall 2020}
        {Teaching Assistant}
        {Yale University}
        {CPSC 422/522: OS Design and Implementation}
        {}
        {Instructor: Zhong Shao}
\cventry{Spring 2020}
        {Teaching Assistant}
        {Yale University}
        {CPSC 421/521: Compilers and Interpreters}
        {}
        {Instructor: Robert Soul{\'e}}
\cventry{Fall 2019}
        {Teaching Assistant}
        {Yale University}
        {CPSC 422/522: OS Design and Implementation}
        {}
        {Instructor: Zhong Shao}
\cventry{Fall 2018}
        {Teaching Assistant}
        {Yale University}
        {CPSC 422/522: OS Design and Implementation}
        {}
        {Instructor: Zhong Shao}
\cventry{Fall 2017}
        {Teaching Assistant}
        {Yale University}
        {CPSC 431/531: Algorithmic Computer Music}
        {}
        {Instructor: Scott Petersen}
\cventry{Spring 2016}
        {Teaching Assistant}
        {University of Rochester}
        {CSC 252: Computer Organization}
        {}
        {Instructor: Engin Ipek}
\cventry{Fall 2015}
        {Teaching Assistant}
        {University of Rochester}
        {CSC 171: The Science of Programming}
        {}
        {Instructor: George Ferguson}
\cventry{Spring 2015}
        {Teaching Assistant}
        {University of Rochester}
        {CSC 172: The Science of Data Structures}
        {}
        {Instructor: Ted Pawlicki}

\section{Honors and Awards}

\cventry{2016}{Graduated \textit{Summa Cum Laude}}{University of Rochester}{}{}{}
\cventry{Joined 2015}{Phi Beta Kappa member}{Iota Chapter}{}{}{}
\cventry{2012--2016}{Dean's List}{University of Rochester}{}{}{}
\cventry{2012}{Wilder Trustee Scholarship}{University of Rochester}{}{}{}

\nocite{*}
\bibliographystyle{unsrt}
\bibliography{pubs}

\end{document}
